Constant-round Blind Classical Verification of Quantum Sampling

### 2020-04-14 hamiltonian.tex

One, however, needs to combine the test and the output on multiple copies of the history states for our second purpose, where we construct the following cut-and-choose protocol.  
% At a high level, it is a cut-and-choose protocol.
% The server constructs multiple copies of the ground state as certificates,
% then the client randomly chooses a copy to output and checks the rest.
% Unfortunately our approach incurs inverse polynomial soundness errors.
% There are two main challenges to this cut-and-choose approach.
% First, the client needs to reliably extract the circuit output from its corresponding ground state.
% We accomplish this by padding the circuit with identity gates at the end.
% By doing so, the clock register collapses to after the last non-identity gate with high probability.

The other challenge is that a cheating prover's certificates can be arbitrarily entangled,
so common techniques such as Chernoff bounds can't be applied as-is.
This wasn't a challenge for $\Piblind$ for $\BQP$ earlier because...
\Ethan{TODO; need brief and intuitive explanation}
In our case with $\SampBQP$, we overcome this challenge instead by using de Finetti's theorem
to approximate our measurement results with that of some unentangled copies,
within inverse polynomial errors.

>>>>

To serve the second purpose, one needs to combine the test and the output on multiple copies of the history states, where we construct the following cut-and-choose protocol.  
% At a high level, it is a cut-and-choose protocol.
% The server constructs multiple copies of the ground state as certificates,
% then the client randomly chooses a copy to output and checks the rest.
% Unfortunately our approach incurs inverse polynomial soundness errors.
% There are two main challenges to this cut-and-choose approach.
% First, the client needs to reliably extract the circuit output from its corresponding ground state.
% We accomplish this by padding the circuit with identity gates at the end.
% By doing so, the clock register collapses to after the last non-identity gate with high probability.
The challenge comes from the fact that a cheating prover might send something rather than copies of the history state. 
In particular, the prover can entangle between different copies in order to cheat. 
In the case of certifying a $\BQP$ computation, the goal is to verify the ground energy of any local Hamiltonian. 
A cheating strategy with potential entanglement won't create any witness state with energy lower than the actual ground energy. 
Thus, this kind of attack won't work for $B$

one always needs to send the best certificate state (i.e., the perfect history state) in order to pass the local Hamiltonian ground energy test.

The other challenge is that a cheating prover's certificates can be arbitrarily entangled,
so common techniques such as Chernoff bounds can't be applied as-is.

%This wasn't a challenge for $\Piblind$ for $\BQP$ earlier because...

In our case with $\SampBQP$, we overcome this challenge instead by using de Finetti's theorem

to approximate our measurement results with that of some unentangled copies,
within inverse polynomial errors.
